### 2023-12-26 documentation/thesis/thesis_document.tex
more thesis

\ref{1D_sensor_schematic_and_circuit_board.png}

\begin{itemize}
\tightlist
\item
  usb
\item
  multiplexer for i2c sensors alredy implemented
\item
  imput / output for sync
\end{itemize}

@@

Next, the subsystem for multi-sensor
synchronisation\ref{sensor-syncronsisation-interface} is set up. The
last step in the setup is to set up communication with the host or
connected \gls{pc}. All microcontroller platforms used here have a
\gls{usb} slave port. The used usb descriptor is
\passthrough{\lstinline!Serial over (+usb)!}-((+usb)\gls{cdc}). This is
used to emulate a virtual RS232 communication port using a USB port on a
\gls{pc} and usually no additional driver is needed on modern systems.

@@

Each sensor that has been loaded with the firmware, registeres on to the
host \gls{pc} as a serial interface. There are several ways for the user
to interact with this:

@@

The \gls{cli} mode is a simple text-based interface with which it is
possible to read out current measured values, obtain debug information
and set operating parameters. This allows you to quickly determine
whether the hardware is working properly after installation. The
\gls{cli} behaves like terminal programmes, displaying a detailed
command reference\ref{Sensors_(+cli).png} to the user after connecting.
The current measured value can be output using the
\passthrough{\lstinline!readout!}
command\ref{Query_sensors_b_value_using_(+cli).png}.

@@

The other option is to use the \gls{mrp}-library. The serial interface
is also used here. However, after a connection attempt by the
\passthrough{\lstinline!MRPHal!} module\ref{hal} of the
\gls{mrp}-library, the system switches to binary mode, which is
initiated using the \passthrough{\lstinline!sbm!} command. However, the
same commands are available as for \gls{cli}-based communication.

@@

\begin{longtable}[]{@{}llllll@{}}
\caption{Measured sensor readout to processing using host software
\label{Measured_sensor_readout_to_processing_using_host_software.csv}}\tabularnewline
\toprule
\begin{minipage}[b]{0.02\columnwidth}\raggedright
Run\strut
\end{minipage} & \begin{minipage}[b]{0.06\columnwidth}\raggedright
Datapoints\strut
\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\raggedright
Host software runtime {[}ms{]}\strut
\end{minipage} & \begin{minipage}[b]{0.29\columnwidth}\raggedright
Average Sensor communication time per reading {[}ms{]}\strut
\end{minipage} & \begin{minipage}[b]{0.18\columnwidth}\raggedright
Communication jitter time {[}ms{]}\strut
\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedright
Comment\strut
\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.02\columnwidth}\raggedright
Run\strut
\end{minipage} & \begin{minipage}[b]{0.06\columnwidth}\raggedright
Datapoints\strut
\end{minipage} & \begin{minipage}[b]{0.15\columnwidth}\raggedright
Host software runtime {[}ms{]}\strut
\end{minipage} & \begin{minipage}[b]{0.29\columnwidth}\raggedright
Average Sensor communication time per reading {[}ms{]}\strut
\end{minipage} & \begin{minipage}[b]{0.18\columnwidth}\raggedright
Communication jitter time {[}ms{]}\strut
\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedright
Comment\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.02\columnwidth}\raggedright
1\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
1\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
9453\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
1.44\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
0\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright
2\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
1\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
9864\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
1.5\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
0\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright
3\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
10\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
12984\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
1.22\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
0.9\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright
4\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
10\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
12673\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
1.13\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
1.1\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright
5\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
10\strut
\end{minipage} & \begin{minipage}[t]{0.15\columnwidth}\raggedright
43264\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright
2.19\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedright
4.2\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
High host system cpu load\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

Since the \passthrough{\lstinline!MMC5603NJ!} only has very limited
measuring range, even small neodymium magnets already saturate this
range, it is possible to use 3D-printed spacers above the sensor.

@@

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following section shows how existing hardware can be
integrated into the system. This is shown here using a
temperature-compensated \passthrough{\lstinline!Voltcraft GM-70!}
telsameter\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png},
which has a measuring range of \passthrough{\lstinline!0-3T!} with a
resolution of 0.1mT. This offers an \passthrough{\lstinline!RS232!}
interface with a documented
protocol\ref{Voltcraft_GM70_serial_protocol.csv} for connection to a
\gls{pc}. This connectivity makes it possible to make the device
compatible with the \gls{mrp} library using interface software
\cite{VoltcraftGM70Rest} executable on the host \gls{pc}. However,
it does not offer the range of functions that the
\passthrough{\lstinline!Unified Sensor Firmware!}\ref{firmware} offers.

@@

At the current state of implementation, it is only possible to detect
and use sensors that are directly connected to the \gls{pc} with the
\gls{mrp}-library. This has the disadvantage that there must always be a
physical connection. This can make it difficult to install multiple
sensors in measurement setups where space or cable routing options are
limited. To make sensors connected to a small
\passthrough{\lstinline!remote!} \gls{pc} available on the network, the
\passthrough{\lstinline!Proxy!}\ref{MRPlib_Proxy_Module.png} module has
been developed. This can be a \gls{sbc} (e.g.~a Raspberry Pi). The small
footprint and low power consumption make it a good choice. It can also
be used in a temperature chamber. The approach of implementing this via
a \gls{rest} interface also offers the advantage that several
measurements or experiments can be recorded at the same time with the
sensors.

@@

If time-critical synchronisation is required, \gls{ptp} and \gls{pps}
output functionality can be used on many \gls{sbc}, such as the
\passthrough{\lstinline!Raspberry-Pi Compute Module 4!}.

\begin{itemize}
\tightlist
\item
  was ptp, bild pps output
\item
  alle clients über ptp verbunden
\item
  dso bild von jeff gerling über rpi4 ptp
\end{itemize}

@@

One important point that improves usability for users is the simple
installation of the \gls{mrp}-library. As it was created in the Python
programming language, there are several public package directories where
users can provide their software modules. Here,
\passthrough{\lstinline!PyPi!}\cite{PyPI}\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png}\cite{MagneticReadoutProcessingPyPI}
is the most commonly used package directory and offers direct support
for the package installation programm
\gls{pip}\ref{lst:setup_lib_with_pip}.

@@

To make the \gls{mrp}-library compatible with the package directory,
Python provides separate installation routines that build a package in
an isolated environment and then provide an installation
\passthrough{\lstinline!wheel!} archive. This can then be uploaded to
the package directory.

@@

Since `docstrings' only document the source code, but do not provide
simple how-to-use instructions, the documentation framework
\passthrough{\lstinline!Sphinx!}\cite{SphinxDocumentation} was used
for this purpose. This framework makes it possible to generate
\gls{html} or \gls{pdf} documentation from various source code
documentation formats, such as the used
\passthrough{\lstinline!docstrings!}. These are converted into a
Markdown format in an intermediate step and this also allows to add
further user documentation such as examples or installation
instructions.

In order to make the documentation created by
\passthrough{\lstinline!Sphinx!} accessible to the user, there are, as
with the package management by \passthrough{\lstinline!PyPi!} services,
which provide Python \gls{mrp}-library documentation online.

@@

\hypertarget{prequesites-for-evaluation}{%
\section{Prequesites for evaluation}\label{prequesites-for-evaluation}}

@@

\hypertarget{evaluation-confiugration}{%
\section{Evaluation confiugration}\label{evaluation-confiugration}}

\hypertarget{sensor-readout}{%
\subsection{Sensor readout}\label{sensor-readout}}

\hypertarget{processing-pipeline}{%
\subsection{Processing pipeline}\label{processing-pipeline}}

\hypertarget{test-scenarios}{%
\section{Test scenarios}\label{test-scenarios}}

\hypertarget{results}{%
\section{Results}\label{results}}

>>>>

As with the mechanical design, the electronics should be kept as simple
as possible so that it is possible to use the microcontroller and a
magnetic field sensor.

The focus here was on utilising existing microcontroller development and
evaluation boards, which already integrate all the components required
for smooth operation. This not only enabled a time-saving
implementation, but also ensured a cost-efficient realisation.

A decisive step in my work was the in-house PCB
design\ref{1D_sensor_schematic_and_circuit_board.png}, which leads out
all the important connections. The placement and alignment of the
components optimised the wiring, which in turn improved the reliability
of the sensor tests. Particular attention was paid to the implementation
of a \passthrough{\lstinline!SYNC!}-\gls{gpio}, which enables subsequent
multi-sensor synchronisation. This functionality opens up the
possibility of synchronising data from different sensors to achieve
precise and coherent measurement results. Overall, this integrated
approach represents an effective solution for the flexible evaluation of
sensors and helps to optimise the development process.

@@

Next, the subsystem for multi-sensor
synchronisation\ref{sensor-syncronsisation-interface} is set up. The
last step in the setup is to set up communication with the host or
connected \gls{pc}. All microcontroller platforms used here have a
\gls{usb} slave port. The used usb descriptor is
\passthrough{\lstinline!Serial over (+usb)!}-((+usb)\gls{cdc}). This is
used to emulate a virtual RS232 communication port using a \gls{usb}
port on a \gls{pc} and usually no additional driver is needed on modern
systems.

@@

Each sensor that has been loaded with the firmware, registeres on to the
host \gls{pc} as a serial interface. There are several ways for the user
to interact with the sensor:

@@

The \gls{cli} mode is a simple text-based interface with which it is
possible to read out current measured values, obtain debug information
and set operating parameters. This allows to quickly determine whether
the hardware is working properly after installation. The \gls{cli}
behaves like terminal programmes, displaying a detailed command
reference\ref{Sensors_(+cli).png} to the user after connecting. The
current measured value can be output using the
\passthrough{\lstinline!readout!}
command\ref{Query_sensors_b_value_using_(+cli).png}.

@@

The other option is to use the \gls{mrp}-library. The serial interface
is also used here. However, after a connection attempt by the
\passthrough{\lstinline!MRPHal!} module\ref{hal} of the
\gls{mrp}-library, the system switches to binary mode, which is
initiated using the \passthrough{\lstinline!sbm!} command. The same
commands are available as for \gls{cli}-based communication.

@@

\begin{longtable}[]{@{}llllll@{}}
\caption{Measured sensor readout to processing using host software
\label{Measured_sensor_readout_to_processing_using_host_software.csv}}\tabularnewline
\toprule
\begin{minipage}[b]{0.02\columnwidth}\raggedright
Run\strut
\end{minipage} & \begin{minipage}[b]{0.04\columnwidth}\raggedright
Points\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright
Host software runtime {[}ms{]}\strut
\end{minipage} & \begin{minipage}[b]{0.32\columnwidth}\raggedright
Average Sensor communication time per reading {[}ms{]}\strut
\end{minipage} & \begin{minipage}[b]{0.20\columnwidth}\raggedright
Communication jitter time {[}ms{]}\strut
\end{minipage} & \begin{minipage}[b]{0.09\columnwidth}\raggedright
Comment\strut
\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.02\columnwidth}\raggedright
Run\strut
\end{minipage} & \begin{minipage}[b]{0.04\columnwidth}\raggedright
Points\strut
\end{minipage} & \begin{minipage}[b]{0.16\columnwidth}\raggedright
Host software runtime {[}ms{]}\strut
\end{minipage} & \begin{minipage}[b]{0.32\columnwidth}\raggedright
Average Sensor communication time per reading {[}ms{]}\strut
\end{minipage} & \begin{minipage}[b]{0.20\columnwidth}\raggedright
Communication jitter time {[}ms{]}\strut
\end{minipage} & \begin{minipage}[b]{0.09\columnwidth}\raggedright
Comment\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.02\columnwidth}\raggedright
1\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
1\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
9453\strut
\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
1.44\strut
\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedright
0\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright
2\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
1\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
9864\strut
\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
1.5\strut
\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedright
0\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright
3\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
10\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
12984\strut
\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
1.22\strut
\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedright
0.9\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright
4\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
10\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
12673\strut
\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
1.13\strut
\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedright
1.1\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.02\columnwidth}\raggedright
5\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
10\strut
\end{minipage} & \begin{minipage}[t]{0.16\columnwidth}\raggedright
43264\strut
\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
2.19\strut
\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedright
8.2\strut
\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright
96\% system load\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

Since the \passthrough{\lstinline!MMC5603NJ!} only has very limited
measuring range, even small neodymium magnets already saturate its
range, it is possible to use 3D-printed spacers above the sensor.

@@

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following section shows how existing hardware can be
integrated into the system. This is shown here using a
temperature-compensated \passthrough{\lstinline!Voltcraft GM-70!}
telsameter\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png},
which has a measuring range of \passthrough{\lstinline!0-3T!} with a
resolution of 0.1mT. It offers an \passthrough{\lstinline!RS232!}
interface with a documented
protocol\ref{Voltcraft_GM70_serial_protocol.csv} for connection to a
\gls{pc}. This connectivity makes it possible to make the device
compatible with the \gls{mrp} library using interface software
\cite{VoltcraftGM70Rest} executable on the host \gls{pc}. However,
it does not offer the range of functions that the
\passthrough{\lstinline!Unified Sensor Firmware!}\ref{firmware} offers.

@@

At the current state of implementation, it is only possible to detect
and use sensors that are directly connected to the \gls{pc} with the
\gls{mrp}-library. It has the disadvantage that there must always be a
physical connection. This can make it difficult to install multiple
sensors in measurement setups where space or cable routing options are
limited. To make sensors connected to a small
\passthrough{\lstinline!remote!} \gls{pc} available on the network, the
\passthrough{\lstinline!Proxy!}\ref{MRPlib_Proxy_Module.png} module has
been developed. This can be a \gls{sbc} (e.g.~a Raspberry Pi). The small
footprint and low power consumption make it a good choice. It can also
be used in a temperature chamber. The approach of implementing this via
a \gls{rest} interface also offers the advantage that several
measurements or experiments can be recorded at the same time with the
sensors.

@@

If time-critical synchronisation over the network is required, \gls{ptp}
and \gls{pps} output functionality\cite{PTPIEEE1588} can be used on
many \gls{sbc}, such as the
\passthrough{\lstinline!Raspberry-Pi Compute Module 4!}.

@@

One important point that improves usability for users is the simple
installation of the \gls{mrp}-library. As it was created in the Python
programming language, there are several public package registry where
users can provide their software modules. Here,
\passthrough{\lstinline!PyPi!}\cite{PyPI}\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png}\cite{MagneticReadoutProcessingPyPI}
is the most commonly used package registry and offers direct support for
the package installation programm \gls{pip}\ref{lst:setup_lib_with_pip}.

@@

To make the \gls{mrp}-library compatible with the package registry,
Python provides separate installation routines that build a package in
an isolated environment and then provide an installation
\passthrough{\lstinline!wheel!} archive. This can then be uploaded to
the package registry.

@@

Since `docstrings' only document the source code, but do not provide
simple how-to-use instructions, the documentation framework
\passthrough{\lstinline!Sphinx!}\cite{SphinxDocumentation} was used
for this purpose. This framework makes it possible to generate
\gls{html} or \gls{pdf} documentation from various source code
documentation formats, such as the used
\passthrough{\lstinline!docstrings!}. These are converted into a
Markdown format in an intermediate step and this also allows to add
further user documentation such as examples or installation
instructions. In order to make the documentation created by
\passthrough{\lstinline!Sphinx!} accessible to the user, there are, as
with the package management by \passthrough{\lstinline!PyPi!} services,
which provide Python \gls{mrp}-library documentation online.

@@

This work successfully implemented a universal hardware and software
framework for the automated characterisation of permanent magnets. This
framework consists of a low-cost hardware interface that supports
various magnetic field sensors and a library for automating and
analysing the measurement data. The process of this framework comprises
several steps, which I will explain below:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Hardware preperation} Users can prepare measurements using the
  implemented framework. This includes the placement of the sensors and
  the selection of the relevant parameters for the characterisation of
  the permanent magnets.
\item
  \textbf{Configuration of the measurement} The software provides a
  user-friendly interface for configuring the measurement parameters.
  Users can make the desired settings here and customise the framework
  to their specific requirements.
\item
  \textbf{Custom algorithm implementation} An important contribution of
  the \gls{mrp} echosystem is the possibility for users to implement
  their own algorithm for data analysis. This allows customisation to
  specific research questions or experimental requirements.
\item
  \textbf{Execution of analysis pipeline} The analysis pipeline can then
  be executed with the implemented algorithm. The collected measurement
  data is automatically processed and analysed to extract characteristic
  parameters of the permanent magnets.
\end{enumerate}

This process covers all the essential functionalities required for a
comprehensive characterisation of permanent magnets\ref{usecases}. The
developed framework not only offers a cost-effective and flexible
hardware solution, but also enables customisation of the analysis
algorithms to meet the requirements of different research projects.

\hypertarget{hardware-preperation}{%
\section{Hardware preperation}\label{hardware-preperation}}

@@

For the hardware setup, the
\passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere} sensor was
used for the evaulation of the framework. As this is equipped with an
exchangeable magnetic holder mount, suitable holders are required for
the magnets to be measured. Ten random
\passthrough{\lstinline!N45 12x12x12mm!} neodymium magnets were used
here. These were placed in modified 3D printed
holders\ref{testmagnets_in_holder.png} and then numbered. This allows
them to be matched to the measurement results later.

\hypertarget{configuration-of-the-measurement}{%
\section{Configuration of the
measurement}\label{configuration-of-the-measurement}}

The configured hardware was then connected and connected to the host
system using the
\passthrough{\lstinline!MRPcli config setupsensor eval\_measurement\_config!}-\gls{cli}
command. The measurement was then
configured\ref{lst:evaluation_measurement_config}.

\begin{lstlisting}[language=bash, caption={Measurement configuration for evaluation measurement}, label=lst:evaluation_measurement_config]
## CONFIGURE THE MEASUREMENT
$ MRPcli config setup eval_measurement_config
> READING-NAME: 360_eval_magnet_<id>
> OUTPUT-FOLDER: ./readings/evaluation/
> NUMBER DATAPOINTS: 18 # FOR A FULLSPHERE READING USE MULTIBLE OF 18
> NUMBER AVERAGE READINGS PER DATAPOINT: 10
\end{lstlisting}

The \passthrough{\lstinline!MRPcli measure run!} command was then called
up for each individual magnet to carry out a measurement. After each
run, the \passthrough{\lstinline!READING-NAME!} parameter was filled
with the id of the next magnet so that all measurements could be
assigned to the physical magnets.

\hypertarget{custom-algorithm-implementation}{%
\section{Custom algorithm
implementation}\label{custom-algorithm-implementation}}

The next step for the user is the implementation of the filter
algorithm\ref{lst:custom_find_similar_values_algorithm}. This can have
any function signature and is implemented in the file
\passthrough{\lstinline!UDPPFunctionCollection.py!}. This Python file is
loaded when the pipeline is started and all functions that are imported
here as a module or implemented directly can be called via the pipeline.
As this is a short algorithm, it was inserted directly into the file.
The parameter \passthrough{\lstinline!\_readings!} should later receive
the imported measurements from the
\passthrough{\lstinline!stage import!} and the optional
\passthrough{\lstinline!IP\_return\_count!} parameter specifies the
number of best measurements that are returned. The return parameter is a
list of measurements and should contain the measurements that are
closest to the mean value of all measurements after the function has
been executed.

\begin{lstlisting}[language=Python, caption={User implemented custom find most similar readings algorithm}, label=lst:custom_find_similar_values_algorithm]
    @staticmethod
    def customFindSimilarValuesAlgorithm(_readings: [MRPReading.MRPReading], IP_return_count: int = -1) -> [MRPReading.MRPReading]:
        import heapq
        heap = []
        # SET RESULT VALUE COUNT
        IP_return_count = max([int(IP_return_count),len(_readings)])
        if IP_return_count < 0:
            IP_return_count = len(_readings) / 5
        # CALCULATE TARGET VALUE: MEAN FROM ALL VALUES
        target_value = 0.0
        for idx, r in enumerate(_readings):
            mean: float = MRPAnalysis.MRPAnalysis.calculate_mean(r)
            target_value = target_value + mean
        target_value = target_value / len(_readings)
        # PUSH READINGS TO HEAP
        for value in _readings:
            # USE DIFF AS PRIORITY VALUE IN MIN-HEAP
            diff = abs(value - target_value)
            heapq.heappush(heap, (diff, value))
        # RETURN X BEST ITEMS FROM HEAP
        similar_values = [item[1] for item in heapq.nsmallest(IP_return_count, heap)]
        # CLEAN UP USED LIBRARIES AND RETURN RESULT
        del heapq
        return similar_values
\end{lstlisting}

The python \passthrough{\lstinline!heapq!}\cite{heapq} module, which
implements a priority queue, is used for this purpose. The calculated
distances from the mean value of the measurements to the global mean
value are inserted into this queue. Subsequently, as many elements of
the queue are returned as defined by the
\passthrough{\lstinline!IP\_return\_count!} parameter. The actual
sorting was carried out by the queue in the background.

\hypertarget{execution-of-analysis-pipeline}{%
\section{Execution of analysis
pipeline}\label{execution-of-analysis-pipeline}}

Once the filter function has been implemented, it still needs to be
integrated into the analysis
pipeline\ref{lst:pipeline_mrp_evaluation_yaml}. Here, the example
pipeline \ref{example_measurement_analysis_pipeline.png} is simplified
and an additional stage \passthrough{\lstinline!find\_similar\_values!}
has been added, which has set
\passthrough{\lstinline!customFindSimilarValuesAlgorithm!} as the
function to be called. As a final step, the result is used in the
\passthrough{\lstinline!plot\_filtered!} stage for visualisation.

\begin{lstlisting}[caption={User defined processing pipeline using custom implemented filter algorithm}, label=lst:pipeline_mrp_evaluation_yaml]
settings:
  enabled: true
  export_intermediate_results: false
  name: pipeline_mrp_evaluation

stage import:
  function: import_readings
  parameters:
    IP_input_folder: ./readings/evaluation/
    IP_file_regex: 360_(.)*.mag.json

stage find_similar_values:
  function: custom_find_similar_values_algorithm
  parameters:
    _readings: stage import # USE RESULTS FROM import STAGE
    IP_return_count: 4 # RETURN BEST 4 of 10 READINGS

stage plot_filtered:
  function: plot_readings
  parameters:
    readings_to_plot: stage find_similar_values # USE RESULTS FROM find_similar_values STAGE
    IP_export_folder: ./readings/evaluation/plots/plot_filtered/
    IP_plot_headline_prefix:  MRP evaluation - filtered
\end{lstlisting}

The final pipeline has been saved in the pipeline directory as
\passthrough{\lstinline!pipeline\_mrp\_evaluation.yaml!} file and is
ready for execution. This is carried out using the
\passthrough{\lstinline!MRPudpp!}-(cli)\ref{lst:bash_pipeline_mrp_evaluation_yaml}.
After the run has been successfully completed, the results are saved in
the result folder specified in the pipeline using the
\passthrough{\lstinline!IP\_export\_folder!} parameter.

\begin{lstlisting}[language=bash, caption={Bash result log of evaluation pipeline run}, label=lst:bash_pipeline_mrp_evaluation_yaml]
# LIST ACTIVE PIPELINES IN PIPELINE DIRECTORY 
$ MRPudpp pipeline listenabledpipelines
> Found enabled pipelines:
> 1. pipeline_mrp_evaluation.yaml
# EXECUTE THE EVALUATION PIPELINE
$ MRPudpp pipeline run
> loading pipeline pipeline_mrp_evaluation.yaml
> stage nodes: ['import', 'find_similar_values', 'plot_raw', 'plot_filtered']
> =====> stage: import 
> =====> stage: find_similar_values 
> =====> stage plot_filtered 
> Process finished with exit code 0
\end{lstlisting}

The figure \ref{MRP_evaluation_result.png} shows this result. The plot
of the raw measured values is shown on the left. The variance of the
determined \passthrough{\lstinline!Mean [uT]!} mean values is plotted on
ten individual measured values. Here you can see that there are measured
values with larger deviations (see measurement
\passthrough{\lstinline!7:0!},\passthrough{\lstinline!10-2:0!},\passthrough{\lstinline!10-1:0!}).

\begin{figure}
\centering
\includegraphics{./generated_images/border_MRP_evaluation_result.png}
\caption{MRP evaluation result \label{MRP_evaluation_result.png}}
\end{figure}

On the right-hand side\ref{MRP_evaluation_result.png}, the measured
values are plotted as a result of the filter algorithm. As the
\passthrough{\lstinline!IP\_return\_count!} parameter was set to four,
only the four most similar measurements were exported here. It can be
seen from the plotted mean values \passthrough{\lstinline!Mean [uT]!}
that these are closest to the global mean value
\passthrough{\lstinline!208.8 uT!}. The algorithm was thus successfully
executed using the pipeline and the results could be validated.
